---
title: "Open Access Author Fund Report at Your Library"
output: pdf_document
date: "YEAR"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Report_unique <- read.csv("path/to/yourFile")
library(tidyverse)
library(plyr)
library(knitr)
library(magrittr)
library(kableExtra)
library(treemapify)
Report_unique <- filter(Report_unique, Period !=2019)
```

```{r load Report_unique, echo=FALSE}
Author <- plyr::count(Report_unique$Name)
Department <- plyr::count(Report_unique$Department)
```

# Open Access Author Fund

As a leader in open access in Canada, the University of Ottawa has a strong record of supporting open access initiatives.

Since 2010, the Library managed the University’s Open Access Author Fund to support researchers publishing in open access. Over the course of its existence, it funded over `r nrow(Report_unique)` articles by `r nrow(Author)` authors and `r nrow(Department)` departments with money provided by the central administration and substantial additional financial support from the Library’s collections budget. 

This report is a summary of the Open Access Author Fund from 2010 to 2018.

```{r echo=FALSE}
Author_freq <- plyr::count(Author$freq)
names(Author_freq) <- c("# of requests by authors", "freq")
Author_freq %>%
  kable() %>%
  kable_styling(full_width = F)
```

# No. of articles supported per year

```{r echo=FALSE}
Period <- plyr::count(Report_unique$Period)
names(Period) <- c("Year", "Freq.")
Period$Year <- as.character(Period$Year)
ggplot(data=Period, aes(x=Year, y=Freq., group=1)) + geom_line() + geom_point(size=4, shape=20) + geom_text(aes(label=Freq., vjust=-1), size=3) + theme_classic()

#kable(Period) %>%
#  kable_styling(bootstrap_options="striped", full_width=FALSE, position="left")
```

## Year: 2010
### No. of articles supported by faculty

```{r echo=FALSE}
Year_2010 <- filter(Report_unique, Period==2010)
Faculty_2010 <- plyr::count(Year_2010$Faculty)
names(Faculty_2010) <- c("Faculty", "Freq.")

Faculty_2010 <- Faculty_2010 %>% 
  arrange(desc(Freq.)) %>% 
  mutate(percentage = round((Freq./sum(Freq.))*100, 1)) %>%
  mutate(lab.ypos = cumsum(Freq.) - 0.5*Freq.)

Faculty_2010$Faculty <- factor(Faculty_2010$Faculty, levels=Faculty_2010$Faculty[order(Faculty_2010$Freq.)])

ggplot(Faculty_2010, aes(x="", y=Freq., fill=Faculty)) + geom_bar(width=1, stat="identity", color="white") + coord_polar("y", start=0) + theme_void() + geom_text(aes(y=lab.ypos, label=percentage))
```

### No. of articles supported by departments

```{r echo=FALSE}
Department_2010 <- unite(Year_2010, "Fac_Dert", c("Faculty", "Department"))

Department_2010 <- Department_2010 %>%
  dplyr::count(Fac_Dert) %>%
  separate(Fac_Dert, c("Faculty", "Department"), sep="_")

ggplot(Department_2010, aes(area=n, fill=Faculty, subgroup=Faculty)) + geom_treemap() +
  geom_treemap_subgroup_border() + geom_treemap_subgroup_text(color="black", place="centre", grow=T, alpha=0.5, fontface="italic") +
  geom_treemap_text(aes(label=Department), reflow=T, min.size=2, color="white") + theme(legend.position="none")

```

### No. of publishers 

```{r echo=FALSE}
Publisher_2010 <- plyr::count(Year_2010$Publisher)

ggplot(Publisher_2010, aes(x=x, y=freq)) + geom_bar(stat="identity", fill="blue") + theme(axis.text.x=element_text(angle=90, vjust=0.5), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank()) 

```

## Year: 2011

### No. of articles supported by faculty

```{r echo=FALSE}
Year_2011 <- filter(Report_unique, Period==2011)
Faculty_2011 <- plyr::count(Year_2011$Faculty)
names(Faculty_2011) <- c("Faculty", "Freq.")

Faculty_2011 <- Faculty_2011 %>% 
  arrange(desc(Freq.)) %>% 
  mutate(percentage = round((Freq./sum(Freq.))*100, 1)) %>%
  mutate(lab.ypos = cumsum(Freq.) - 0.5*Freq.)

Faculty_2011$Faculty <- factor(Faculty_2011$Faculty, levels=Faculty_2011$Faculty[order(Faculty_2011$Freq.)])

ggplot(Faculty_2011, aes(x="", y=Freq., fill=Faculty)) + geom_bar(width=1, stat="identity", color="white") + coord_polar("y", start=0) + theme_void() + geom_text(aes(y=lab.ypos, label=percentage))
```

### No. of articles supported by departments

```{r echo=FALSE}
Department_2011 <- unite(Year_2011, "Fac_Dert", c("Faculty", "Department"))

Department_2011 <- Department_2011 %>%
  dplyr::count(Fac_Dert) %>%
  separate(Fac_Dert, c("Faculty", "Department"), sep="_")

ggplot(Department_2011, aes(area=n, fill=Faculty, subgroup=Faculty)) + geom_treemap() +
  geom_treemap_subgroup_border() + geom_treemap_subgroup_text(color="black", place="centre", grow=T, alpha=0.5, fontface="italic") +
  geom_treemap_text(aes(label=Department), reflow=T, min.size=2, color="white") + theme(legend.position="none")

```

### # of publishers 

```{r echo=FALSE}
Publisher_2011 <- plyr::count(Year_2011$Publisher)

ggplot(Publisher_2011, aes(x=x, y=freq)) + geom_bar(stat="identity", fill="blue") + theme(axis.text.x=element_text(angle=90, vjust=0.5), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank()) 

```

## Year: 2012

### No. of articles supported by faculty

```{r echo=FALSE}
Year_2012 <- filter(Report_unique, Period==2012)
Faculty_2012 <- plyr::count(Year_2012$Faculty)
names(Faculty_2012) <- c("Faculty", "Freq.")

Faculty_2012 <- Faculty_2012 %>% 
  arrange(desc(Freq.)) %>% 
  mutate(percentage = round((Freq./sum(Freq.))*100, 1)) %>%
  mutate(lab.ypos = cumsum(Freq.) - 0.5*Freq.)

Faculty_2012$Faculty <- factor(Faculty_2012$Faculty, levels=Faculty_2012$Faculty[order(Faculty_2012$Freq.)])

ggplot(Faculty_2012, aes(x="", y=Freq., fill=Faculty)) + geom_bar(width=1, stat="identity", color="white") + coord_polar("y", start=0) + theme_void() + geom_text(aes(y=lab.ypos, label=percentage))
```

### No. of articles supported by departments

```{r echo=FALSE}
Department_2012 <- unite(Year_2012, "Fac_Dert", c("Faculty", "Department"))

Department_2012 <- Department_2012 %>%
  dplyr::count(Fac_Dert) %>%
  separate(Fac_Dert, c("Faculty", "Department"), sep="_")

ggplot(Department_2012, aes(area=n, fill=Faculty, subgroup=Faculty)) + geom_treemap() +
  geom_treemap_subgroup_border() + geom_treemap_subgroup_text(color="black", place="centre", grow=T, alpha=0.5, fontface="italic") +
  geom_treemap_text(aes(label=Department), reflow=T, min.size=2, color="white") + theme(legend.position="none")

```

### No. of publishers 

```{r echo=FALSE}
Publisher_2012 <- plyr::count(Year_2012$Publisher)

ggplot(Publisher_2012, aes(x=x, y=freq)) + geom_bar(stat="identity", fill="blue") + theme(axis.text.x=element_text(angle=90, vjust=0.5), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank()) 

```

## Year: 2013

### No. of articles supported by faculty

```{r echo=FALSE}
Year_2013 <- filter(Report_unique, Period==2013)
Faculty_2013 <- plyr::count(Year_2013$Faculty)
names(Faculty_2013) <- c("Faculty", "Freq.")

Faculty_2013 <- Faculty_2013 %>% 
  arrange(desc(Freq.)) %>% 
  mutate(percentage = round((Freq./sum(Freq.))*100, 1)) %>%
  mutate(lab.ypos = cumsum(Freq.) - 0.5*Freq.)

Faculty_2013$Faculty <- factor(Faculty_2013$Faculty, levels=Faculty_2013$Faculty[order(Faculty_2013$Freq.)])

ggplot(Faculty_2013, aes(x="", y=Freq., fill=Faculty)) + geom_bar(width=1, stat="identity", color="white") + coord_polar("y", start=0) + theme_void() + geom_text(aes(y=lab.ypos, label=percentage))
```

### No. of articles supported by departments

```{r echo=FALSE}
Department_2013 <- unite(Year_2013, "Fac_Dert", c("Faculty", "Department"))

Department_2013 <- Department_2013 %>%
  dplyr::count(Fac_Dert) %>%
  separate(Fac_Dert, c("Faculty", "Department"), sep="_")

ggplot(Department_2013, aes(area=n, fill=Faculty, subgroup=Faculty)) + geom_treemap() +
  geom_treemap_subgroup_border() + geom_treemap_subgroup_text(color="black", place="centre", grow=T, alpha=0.5, fontface="italic") +
  geom_treemap_text(aes(label=Department), reflow=T, min.size=2, color="white") + theme(legend.position="none")

```

### No. of publishers 

```{r echo=FALSE}
Publisher_2013 <- plyr::count(Year_2013$Publisher)

ggplot(Publisher_2013, aes(x=x, y=freq)) + geom_bar(stat="identity", fill="blue") + theme(axis.text.x=element_text(angle=90, vjust=0.5), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank()) 

```

## Year: 2014

### No. of articles supported by faculty

```{r echo=FALSE}
Year_2014 <- filter(Report_unique, Period==2014)
Faculty_2014 <- plyr::count(Year_2014$Faculty)
names(Faculty_2014) <- c("Faculty", "Freq.")

Faculty_2014 <- Faculty_2014 %>% 
  arrange(desc(Freq.)) %>% 
  mutate(percentage = round((Freq./sum(Freq.))*100, 1)) %>%
  mutate(lab.ypos = cumsum(Freq.) - 0.5*Freq.)

Faculty_2014$Faculty <- factor(Faculty_2014$Faculty, levels=Faculty_2014$Faculty[order(Faculty_2014$Freq.)])

ggplot(Faculty_2014, aes(x="", y=Freq., fill=Faculty)) + geom_bar(width=1, stat="identity", color="white") + coord_polar("y", start=0) + theme_void() + geom_text(aes(y=lab.ypos, label=percentage))
```

### No. of articles supported by departments

```{r echo=FALSE}
Department_2014 <- unite(Year_2014, "Fac_Dert", c("Faculty", "Department"))

Department_2014 <- Department_2014 %>%
  dplyr::count(Fac_Dert) %>%
  separate(Fac_Dert, c("Faculty", "Department"), sep="_")

ggplot(Department_2014, aes(area=n, fill=Faculty, subgroup=Faculty)) + geom_treemap() +
  geom_treemap_subgroup_border() + geom_treemap_subgroup_text(color="black", place="centre", grow=T, alpha=0.5, fontface="italic") +
  geom_treemap_text(aes(label=Department), reflow=T, min.size=2, color="white") + theme(legend.position="none")

```

### No. of publishers 

```{r echo=FALSE}
Publisher_2014 <- plyr::count(Year_2014$Publisher)

ggplot(Publisher_2014, aes(x=x, y=freq)) + geom_bar(stat="identity", fill="blue") + theme(axis.text.x=element_text(angle=90, vjust=0.5), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank()) 

```

## Year: 2016

### No. of articles supported by faculty

```{r echo=FALSE}
Year_2016 <- filter(Report_unique, Period==2016)
Faculty_2016 <- plyr::count(Year_2016$Faculty)
names(Faculty_2016) <- c("Faculty", "Freq.")

Faculty_2016 <- Faculty_2016 %>% 
  arrange(desc(Freq.)) %>% 
  mutate(percentage = round((Freq./sum(Freq.))*100, 1)) %>%
  mutate(lab.ypos = cumsum(Freq.) - 0.5*Freq.)

Faculty_2016$Faculty <- factor(Faculty_2016$Faculty, levels=Faculty_2016$Faculty[order(Faculty_2016$Freq.)])

ggplot(Faculty_2016, aes(x="", y=Freq., fill=Faculty)) + geom_bar(width=1, stat="identity", color="white") + coord_polar("y", start=0) + theme_void() + geom_text(aes(y=lab.ypos, label=percentage))
```

### No. of articles supported by departments

```{r echo=FALSE}
Department_2016 <- unite(Year_2016, "Fac_Dert", c("Faculty", "Department"))

Department_2016 <- Department_2016 %>%
  dplyr::count(Fac_Dert) %>%
  separate(Fac_Dert, c("Faculty", "Department"), sep="_")

ggplot(Department_2016, aes(area=n, fill=Faculty, subgroup=Faculty)) + geom_treemap() +
  geom_treemap_subgroup_border() + geom_treemap_subgroup_text(color="black", place="centre", grow=T, alpha=0.5, fontface="italic") +
  geom_treemap_text(aes(label=Department), reflow=T, min.size=2, color="white") + theme(legend.position="none")

```

### No. of publishers 

```{r echo=FALSE}
Publisher_2016 <- plyr::count(Year_2016$Publisher)

ggplot(Publisher_2016, aes(x=x, y=freq)) + geom_bar(stat="identity", fill="blue") + theme(axis.text.x=element_text(angle=90, vjust=0.5), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank()) 

```

## Year: 2017

### No. of articles supported by faculty

```{r echo=FALSE}
Year_2017 <- filter(Report_unique, Period==2017)
Faculty_2017 <- plyr::count(Year_2017$Faculty)
names(Faculty_2017) <- c("Faculty", "Freq.")

Faculty_2017 <- Faculty_2017 %>% 
  arrange(desc(Freq.)) %>% 
  mutate(percentage = round((Freq./sum(Freq.))*100, 1)) %>%
  mutate(lab.ypos = cumsum(Freq.) - 0.5*Freq.)

Faculty_2017$Faculty <- factor(Faculty_2017$Faculty, levels=Faculty_2017$Faculty[order(Faculty_2017$Freq.)])

ggplot(Faculty_2017, aes(x="", y=Freq., fill=Faculty)) + geom_bar(width=1, stat="identity", color="white") + coord_polar("y", start=0) + theme_void() + geom_text(aes(y=lab.ypos, label=percentage))
```

### No. of articles supported by departments

```{r echo=FALSE}
Department_2017 <- unite(Year_2017, "Fac_Dert", c("Faculty", "Department"))

Department_2017 <- Department_2017 %>%
  dplyr::count(Fac_Dert) %>%
  separate(Fac_Dert, c("Faculty", "Department"), sep="_")

ggplot(Department_2017, aes(area=n, fill=Faculty, subgroup=Faculty)) + geom_treemap() +
  geom_treemap_subgroup_border() + geom_treemap_subgroup_text(color="black", place="centre", grow=T, alpha=0.5, fontface="italic") +
  geom_treemap_text(aes(label=Department), reflow=T, min.size=2, color="white") + theme(legend.position="none")

```

### No. of publishers 

```{r echo=FALSE}
Publisher_2017 <- plyr::count(Year_2017$Publisher)

ggplot(Publisher_2017, aes(x=x, y=freq)) + geom_bar(stat="identity", fill="blue") + theme(axis.text.x=element_text(angle=90, vjust=0.5), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank()) 

```


## Year: 2018

### No. of articles supported by faculty

```{r echo=FALSE}
Year_2018 <- filter(Report_unique, Period==2018)
Faculty_2018 <- plyr::count(Year_2018$Faculty)
names(Faculty_2018) <- c("Faculty", "Freq.")

Faculty_2018 <- Faculty_2018 %>% 
  arrange(desc(Freq.)) %>% 
  mutate(percentage = round((Freq./sum(Freq.))*100, 1)) %>%
  mutate(lab.ypos = cumsum(Freq.) - 0.5*Freq.)

Faculty_2018$Faculty <- factor(Faculty_2018$Faculty, levels=Faculty_2018$Faculty[order(Faculty_2018$Freq.)])

ggplot(Faculty_2018, aes(x="", y=Freq., fill=Faculty)) + geom_bar(width=1, stat="identity", color="white") + coord_polar("y", start=0) + theme_void() + geom_text(aes(y=lab.ypos, label=percentage))
```

### No. of articles supported by departments

```{r echo=FALSE}
Department_2018 <- unite(Year_2018, "Fac_Dert", c("Faculty", "Department"))

Department_2018 <- Department_2018 %>%
  dplyr::count(Fac_Dert) %>%
  separate(Fac_Dert, c("Faculty", "Department"), sep="_")

ggplot(Department_2018, aes(area=n, fill=Faculty, subgroup=Faculty)) + geom_treemap() +
  geom_treemap_subgroup_border() + geom_treemap_subgroup_text(color="black", place="centre", grow=T, alpha=0.5, fontface="italic") +
  geom_treemap_text(aes(label=Department), reflow=T, min.size=2, color="white") + theme(legend.position="none")

```

### No. of publishers 

```{r echo=FALSE}
Publisher_2018 <- plyr::count(Year_2018$Publisher)

ggplot(Publisher_2018, aes(x=x, y=freq)) + geom_bar(stat="identity", fill="blue") + theme(axis.text.x=element_text(angle=90, vjust=0.5), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), panel.background=element_blank()) 

```
